---
title: "Accessibility Benchmark — Aquavena for the Visually Impaired"
subtitle: "Comparing adriens.github.io/aquavena vs aquavena.nc"
author: "Adriens"
date: today
lang: en
format:
  pdf:
    pdf-engine: xelatex
    toc: true
    toc-depth: 2
    number-sections: true
    colorlinks: true
    geometry:
      - top=25mm
      - bottom=25mm
      - left=20mm
      - right=20mm
    mainfont: "DejaVu Serif"
    sansfont: "DejaVu Sans"
    monofont: "DejaVu Sans Mono"
    keywords:
      - accessibility
      - visually impaired
      - low vision
      - WCAG
      - visual disability
      - New Caledonia
      - Aquavena
    include-in-header:
      text: |
        \usepackage{fontawesome5}
        \usepackage{xcolor}
        \usepackage{hyperref}
        \usepackage{tikz}
        \usetikzlibrary{positioning}
        \definecolor{teal700}{RGB}{15,118,110}
        \definecolor{teal100}{RGB}{204,251,241}

        % ── Custom title page ───────────────────────────────────────────
        \renewcommand{\maketitle}{%
          \begin{titlepage}
          \centering
          \vspace*{1.5cm}

          {\color{teal700}\fontsize{52}{60}\selectfont\faUniversalAccess}

          \vspace{1.2cm}

          {\color{teal700}\fontsize{24}{30}\selectfont\bfseries
            Accessibility Benchmark\\[0.4em]
            Aquavena for the Visually Impaired}

          \vspace{0.6cm}
          {\color{teal700}\rule{0.6\textwidth}{1.5pt}}
          \vspace{0.6cm}

          {\large\color{gray!60!black}
            Comparing \texttt{adriens.github.io/aquavena} vs \texttt{aquavena.nc}\\[0.3em]
            Web Accessibility~·~Low Vision~·~WCAG 2.1 AA~·~New Caledonia}

          \vspace{2cm}

          {\large\bfseries Adriens}\\[0.5em]
          {\color{teal700}\faTwitter}~\href{https://x.com/rastadidi}{\texttt{x.com/rastadidi}}

          \vspace{0.8cm}
          {\large\today}

          \vspace{1.4cm}

          \begin{center}
          \textbf{Abstract}
          \end{center}
          \begin{center}
          \begin{minipage}{0.85\textwidth}
          \centering\small\itshape
          This report automatically compares the web accessibility of
          \textbf{\textit{adriens.github.io/aquavena}} — designed for visually
          impaired users — against the source website \textbf{\textit{aquavena.nc}},
          a dietetic meal delivery service in New Caledonia. Standard CLI tools
          (pa11y-ci, Lighthouse, axe-core, webhint) are used as a common reference.
          Results show a \textbf{\textit{100/100 Lighthouse score and 0 WCAG 2.1 AA
          errors}} for our site, versus 91/100 and 67~errors for the official website.
          All audit data is persisted in a DuckDB database for longitudinal tracking.
          \end{minipage}
          \end{center}

          \end{titlepage}
          \newpage
        }

        % ── TOC on its own page ─────────────────────────────────────────
        \let\origtoc\tableofcontents
        \renewcommand{\tableofcontents}{\origtoc\clearpage}
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(DBI)
library(duckdb)
library(dplyr)
library(tidyr)
library(ggplot2)
library(jsonlite)
library(kableExtra)
library(patchwork)

REPORTS <- "../reports"
DATA    <- "../data"
dir.create(DATA, showWarnings = FALSE)

theme_set(
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold"), panel.grid.minor = element_blank())
)

AUDIT_DATE <- Sys.Date()
DB_PATH    <- file.path(DATA, "benchmark.duckdb")
```

```{r ingest}
# ── Helper: parse a Lighthouse JSON report into a tidy dataframe ───────────
parse_lh <- function(path, site_label, date) {
  raw   <- fromJSON(path, simplifyVector = FALSE)
  score <- round(raw$categories$accessibility$score * 100)
  refs  <- raw$categories$accessibility$auditRefs
  bind_rows(lapply(refs, function(ref) {
    a <- raw$audits[[ref$id]]
    if (is.null(a)) return(NULL)
    tibble(
      audit_id   = ref$id,
      title      = a$title,
      score      = if (is.null(a$score)) NA_real_ else as.numeric(a$score),
      score_mode = if (is.null(a$scoreDisplayMode)) NA_character_ else a$scoreDisplayMode
    )
  })) |>
    mutate(site = site_label, audit_date = date, lighthouse_score = score)
}

# ── Read raw JSONs ─────────────────────────────────────────────────────────
pa11y_raw <- fromJSON(file.path(REPORTS, "pa11y.json"))

# ── pa11y: flatten issues for our site ────────────────────────────────────
pa11y_rows <- bind_rows(lapply(names(pa11y_raw$results), function(url) {
  issues <- pa11y_raw$results[[url]]
  if (is.null(issues) || length(issues) == 0)
    return(tibble(url = url, type = NA_character_, message = NA_character_,
                  code = NA_character_))
  tibble(url = url, type = issues$type, message = issues$message,
         code = if (!is.null(issues$code)) issues$code else NA_character_)
})) |>
  mutate(site = "our-site", audit_date = AUDIT_DATE)

# ── Lighthouse: our site (full audit detail) ───────────────────────────────
lh_rows <- parse_lh(
  file.path(REPORTS, "lighthouse.report.json"),
  "our-site", AUDIT_DATE
)
lh_score <- lh_rows$lighthouse_score[1]

# ── Lighthouse: aquavena.nc (full audit detail) ────────────────────────────
lh_nc_rows <- parse_lh(
  file.path(REPORTS, "lighthouse-aquavena-nc.report.json"),
  "aquavena.nc", as.Date("2026-05-30")
)

# ── pa11y aquavena.nc (manually collected — 67 known errors) ──────────────
nc_pa11y <- tibble(
  url        = "https://www.aquavena.nc/formules/aqua-mediterraneen",
  type       = "error",
  message    = "(manual pa11y-ci audit)",
  code       = NA_character_,
  site       = "aquavena.nc",
  audit_date = as.Date("2026-05-30"),
  n_dummy    = 67L
) |>
  uncount(n_dummy)

# ── Open / create DuckDB ───────────────────────────────────────────────────
con <- dbConnect(duckdb(), DB_PATH)

if (!dbExistsTable(con, "pa11y_issues")) {
  dbWriteTable(con, "pa11y_issues", bind_rows(pa11y_rows, nc_pa11y))
} else {
  existing <- dbGetQuery(con, "SELECT DISTINCT site, audit_date FROM pa11y_issues")
  new_rows <- bind_rows(pa11y_rows, nc_pa11y) |>
    anti_join(existing, by = c("site", "audit_date"))
  if (nrow(new_rows) > 0) dbAppendTable(con, "pa11y_issues", new_rows)
}

all_lh <- bind_rows(lh_rows, lh_nc_rows)
if (!dbExistsTable(con, "lighthouse_audits")) {
  dbWriteTable(con, "lighthouse_audits", all_lh)
} else {
  existing <- dbGetQuery(con, "SELECT DISTINCT site, audit_date FROM lighthouse_audits")
  new_rows <- all_lh |>
    anti_join(existing, by = c("site", "audit_date"))
  if (nrow(new_rows) > 0) dbAppendTable(con, "lighthouse_audits", new_rows)
}
```

# Inception

This project was not born in a research lab or a corporate accessibility audit.
It started at a kitchen table, from a very simple and concrete situation.

My mother has been a loyal Aquavena customer for years. Every week she orders her
meals from their service, and she genuinely enjoys the food. But she is visually
impaired — and as her condition evolved, consulting the weekly menus on the official
website became increasingly difficult, then impossible to do on her own. The layout,
the font sizes, the colour contrasts, the absence of any audio alternative: none of
it was designed with her in mind.

The consequence was small but recurring, and that is precisely what made it
significant. Every week, she had to wait for someone to be available — a family
member, a neighbour — to read the menus out loud to her. She lost the freedom to
plan her own meals at her own pace. A minor dependency, perhaps, but one that
repeated itself week after week, quietly eroding her autonomy.

I am a software engineer. I realised that a few hours of work could give that
autonomy back to her: a dedicated page she could open on her tablet, with large text,
high contrast, a dark mode for tired eyes, and a button to have the menus read aloud
in her own language. Something she could use alone, at any hour, without asking
anyone for help.

That is why this site exists. It is not a product, not a startup, not a statement.
It is a small act of care, built with the tools I know, for the person who matters
most. The accessibility work documented in this report is a direct consequence of
that intent: if the site is meant to help someone with low vision, it had better
actually be accessible.

A note to the Aquavena team, should they ever read this: there is no competition
here, no monetisation, no hidden agenda. Every menu on this site links back to
[aquavena.nc](https://www.aquavena.nc) to place orders. This is simply a more
accessible front door to a service my mother loves.

# Context

This report compares the accessibility of
[adriens.github.io/aquavena](https://adriens.github.io/aquavena) — designed for
visually impaired users — against the original source website
[aquavena.nc](https://www.aquavena.nc) — using identical, reproducible CLI tools.

# Site Architecture

## Design principles

The companion site was built around a single constraint: every design decision had
to serve a visually impaired user first. Three principles guided the work throughout.

**Readability before aesthetics.** The site uses
[Atkinson Hyperlegible](https://brailleinstitute.org/freefont), a typeface designed
by the Braille Institute specifically to maximise legibility for people with low
vision. Each letterform is engineered to be unambiguous: no `l` that looks like `1`,
no `O` that looks like `0`. The base font size is 18px, adjustable at runtime via
A+ / A− buttons that persist across sessions in `localStorage`.

**Multiple access modalities.** Users should never be forced to read. Every menu can
be listened to via the Web Speech API (text-to-speech), one day at a time or the
entire week in sequence. Menus are also exposed as RSS feeds and iCal calendars so
that a screen reader, a podcast app, or a calendar assistant can consume them without
opening a browser at all.

**Progressive Web App.** The site is installable on any device (iOS, Android,
desktop) and works fully offline once cached, so connectivity issues — relevant in
parts of New Caledonia — do not block access to the weekly menus.

## Technology stack

```{r stack-table}
stack <- tibble::tribble(
  ~Layer,          ~Technology,          ~Role,
  "Framework",     "Astro 4",            "Static site generator — zero JS by default",
  "Styling",       "Tailwind CSS 3",     "Utility-first CSS, WCAG-compliant colour palette",
  "Typography",    "Atkinson Hyperlegible","Typeface designed for low vision",
  "Icons",         "Font Awesome 6",     "Accessible SVG icons with aria-labels",
  "TTS",           "Web Speech API",     "Browser-native text-to-speech, no dependency",
  "PWA",           "Vite PWA / Workbox", "Service worker, offline cache, installability",
  "Data",          "Python + SDK",       "Custom scraper — fetches menus from aquavena.nc",
  "Feeds",         "Astro RSS",          "RSS 2.0 feeds per diet regime",
  "Calendars",     "ical.js",            "iCal (.ics) exports per diet regime",
  "CI/CD",         "GitHub Actions",     "Nightly data fetch + build + deploy to GitHub Pages",
  "AI interface",  "Claude MCP skill",   "Natural-language menu queries via Model Context Protocol"
)
kable(stack, booktabs = TRUE, linesep = "") |>
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10)
```

## Data pipeline

Menus are not hardcoded. A Python SDK scrapes the weekly menus from
[aquavena.nc](https://www.aquavena.nc) each night via a GitHub Actions workflow.
The scraped data is written to `src/data/menus.json`, which Astro consumes at build
time to generate the static HTML pages. The resulting site is deployed to GitHub
Pages with no server-side component.

```
aquavena.nc  →  Python SDK (fetch_data.py)  →  menus.json
                                                    ↓
                                            Astro build  →  GitHub Pages
```

The site is therefore always up to date by the following morning, with no manual
intervention required.

## Accessibility engineering

WCAG 2.1 AA conformance was achieved iteratively, guided by three complementary
tools run after every change: **pa11y-ci** (WCAG rule violations), **Lighthouse**
(scored audit), and **axe-cli** (axe-core engine). The main categories of issues
identified and resolved were:

- **Colour contrast (1.4.3):** All interactive elements — speak buttons, tab labels,
  action links — were systematically audited. Colours such as `bg-orange-500` and
  `bg-sky-500` were replaced with their `-700` variants to meet the 4.5:1 ratio for
  normal text and 3:1 for large bold text.
- **Landmark regions (4.1.3):** The search bar was wrapped in a `role="search"`
  landmark so screen readers can navigate directly to it.
- **Label in name (2.5.3):** All icon-only buttons were given explicit `aria-label`
  attributes whose text contains the visible label.
- **Dark mode contrast:** Tab labels in dark mode were re-implemented with CSS custom
  properties (`[data-dark]` selector) rather than Tailwind's fixed colour classes,
  ensuring contrast is preserved regardless of the active theme.

# Methodology

## Pipeline overview

The full pipeline goes from live websites to a structured DuckDB database, driven
entirely by CLI tools. Each step produces a JSON artefact that feeds the next.

```{=latex}
\begin{center}
\begin{tikzpicture}[
  node distance=0.55cm and 0.9cm,
  cli/.style  ={draw, rounded corners=4pt, minimum width=2.3cm, minimum height=0.65cm,
                font=\small\sffamily, fill=teal100, draw=teal700, align=center},
  json/.style ={draw, rounded corners=2pt, minimum width=2.3cm, minimum height=0.58cm,
                font=\scriptsize\ttfamily, fill=gray!10, draw=gray!50, align=center},
  db/.style   ={draw, rounded corners=4pt, minimum width=10.2cm, minimum height=0.68cm,
                font=\small\sffamily\bfseries, fill=teal700!20, draw=teal700, align=center},
  pdf/.style  ={draw, rounded corners=4pt, minimum width=10.2cm, minimum height=0.68cm,
                font=\small\sffamily\bfseries, fill=teal700, draw=teal700,
                text=white, align=center},
  arr/.style  ={->, thick, color=teal700}
]
% Row 0 – Python scraper
\node[cli, minimum width=10.2cm] (py) {Python — \texttt{fetch\_data.py} (scrapes menus from aquavena.nc)};

% Row 1 – CLI tools (4 nodes)
\node[cli, below=0.9cm of py, xshift=-3.7cm] (pa11y) {pa11y-ci};
\node[cli, right=of pa11y]  (lhO)  {Lighthouse};
\node[cli, right=of lhO]    (lhNC) {Lighthouse};
\node[cli, right=of lhNC]   (wh)   {webhint};

% Row 1 labels
\node[font=\tiny\itshape, below=0pt of pa11y]  {};
\node[font=\tiny\itshape, above=0pt of lhO,  yshift=1pt]  {};

% Row 2 – JSON files
\node[json, below=0.55cm of pa11y] (j1) {pa11y.json};
\node[json, below=0.55cm of lhO]   (j2) {lighthouse\\our-site.json};
\node[json, below=0.55cm of lhNC]  (j3) {lighthouse\\aquavena-nc.json};
\node[json, below=0.55cm of wh]    (j4) {hint-report/\\*.html};

% Row 3 – DuckDB
\node[db, below=0.9cm of j2, xshift=0.45cm] (duckdb)
  {\faDatabase\quad benchmark.duckdb \quad(\texttt{pa11y\_issues}, \texttt{lighthouse\_audits})};

% Row 4 – PDF
\node[pdf, below=0.55cm of duckdb] (rpdf)
  {\faFilePdf\quad report.pdf \;—\; Quarto + R (ggplot2, kableExtra)};

% Arrows: Python → CLI row
\draw[arr] (py.south) -- ++(0,-0.22) -| (pa11y.north);
\draw[arr] (py.south) -- ++(0,-0.22) -| (lhO.north);
\draw[arr] (py.south) -- ++(0,-0.22) -| (lhNC.north);
\draw[arr] (py.south) -- ++(0,-0.22) -| (wh.north);

% Arrows: CLIs → JSONs
\draw[arr] (pa11y) -- (j1);
\draw[arr] (lhO)   -- (j2);
\draw[arr] (lhNC)  -- (j3);
\draw[arr] (wh)    -- (j4);

% Arrows: JSONs → DuckDB
\draw[arr] (j1.south) -- ++(0,-0.22) -| (duckdb.north);
\draw[arr] (j2.south) -- (duckdb.north);
\draw[arr] (j3.south) -- ++(0,-0.22) -| (duckdb.north);

% DuckDB → PDF
\draw[arr] (duckdb) -- (rpdf);
\end{tikzpicture}
\end{center}
```

## Tools

```{r tools-table}
tools_df <- tibble::tribble(
  ~Tool,           ~Version, ~Purpose,
  "pa11y-ci",      "4.1.1",  "Automated WCAG 2.1 AA audit, multi-URL",
  "Lighthouse",    "13.3.0", "Accessibility score 0–100, 24 audits",
  "axe-cli",       "4.11.3", "axe-core violations via CLI",
  "W3C Validator", "API",    "HTML semantic validation",
  "webhint",       "7.1.13", "Browser compat, security, HTTP headers"
)
kable(tools_df, booktabs = TRUE, linesep = "") |>
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10)
```

## Standard

All automated checks use **WCAG 2.1 Level AA** with both axe-core and htmlcs runners
to maximise coverage.

# Results — Our Site

```{r query-our-site}
total_errors <- dbGetQuery(con, "
  SELECT COUNT(*) AS n FROM pa11y_issues
  WHERE site = 'our-site' AND type = 'error'
    AND audit_date = (SELECT MAX(audit_date) FROM pa11y_issues WHERE site = 'our-site')
")$n

lh_our <- dbGetQuery(con, "
  SELECT lighthouse_score,
         SUM(CASE WHEN score = 1.0 THEN 1 ELSE 0 END) AS passed,
         SUM(CASE WHEN score = 0.0 THEN 1 ELSE 0 END) AS failed,
         SUM(CASE WHEN score_mode = 'notApplicable' THEN 1 ELSE 0 END) AS na_count
  FROM lighthouse_audits
  WHERE site = 'our-site'
    AND audit_date = (SELECT MAX(audit_date) FROM lighthouse_audits WHERE site = 'our-site')
  GROUP BY lighthouse_score
  LIMIT 1
")
lh_score_val <- if (nrow(lh_our) > 0) lh_our$lighthouse_score[[1]] else lh_score
```

## pa11y-ci — WCAG 2.1 AA

```{r pa11y-our-table}
pa11y_display <- dbGetQuery(con, "
  SELECT url,
         SUM(CASE WHEN type = 'error'   THEN 1 ELSE 0 END) AS Errors,
         SUM(CASE WHEN type = 'warning' THEN 1 ELSE 0 END) AS Warnings
  FROM pa11y_issues
  WHERE site = 'our-site'
    AND audit_date = (SELECT MAX(audit_date) FROM pa11y_issues WHERE site = 'our-site')
  GROUP BY url
")

if (nrow(pa11y_display) == 0)
  pa11y_display <- data.frame(url = "All URLs", Errors = 0L, Warnings = 0L)

kable(pa11y_display, booktabs = TRUE, linesep = "",
      col.names = c("URL", "Errors", "Warnings")) |>
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 9)
```

**Total: `r total_errors` error(s)**

## Lighthouse Accessibility

```{r lighthouse-gauge, fig.height=2.8, fig.width=5, fig.align="center"}
gauge_df <- tibble(
  label = c("Score", "Rest"),
  value = c(lh_score_val, 100 - lh_score_val),
  fill  = c("#0f766e", "#e5e7eb")
)
ggplot(gauge_df, aes(x = 2, y = value, fill = fill)) +
  geom_col(width = 1, color = "white") +
  coord_polar(theta = "y", start = pi) +
  xlim(0.5, 2.5) +
  scale_fill_identity() +
  annotate("text", x = 0.5, y = 0,
           label = paste0(lh_score_val, "/100"),
           size = 9, fontface = "bold", color = "#0f766e") +
  annotate("text", x = 0.5, y = -20,
           label = "Lighthouse Accessibility", size = 3.5, color = "grey40") +
  theme_void()
```

```{r lighthouse-details}
lh1 <- if (nrow(lh_our) > 0) lh_our[1, ] else
  data.frame(lighthouse_score = lh_score_val, passed = NA, failed = NA, na_count = NA)
tibble(
  Metric = c("Score", "Passed audits", "Failed audits", "Not applicable"),
  Value  = c(paste0(lh1$lighthouse_score, "/100"),
             as.character(lh1$passed),
             as.character(lh1$failed),
             as.character(lh1$na_count))
) |>
  kable(booktabs = TRUE, linesep = "") |>
  kable_styling(latex_options = "hold_position", font_size = 10, full_width = FALSE)
```

# Results — aquavena.nc

```{r nc-table}
nc_summary <- tibble(
  Tool                       = c("pa11y-ci (WCAG 2.1 AA)", "Lighthouse Accessibility",
                                 "webhint — errors", "webhint — warnings", "webhint — hints"),
  `aquavena.nc`              = c("67 errors", "91/100", "10", "63", "120"),
  `Our site`                 = c("0 errors",  "100/100", "10*", "62", "120")
)
kable(nc_summary, booktabs = TRUE, linesep = "") |>
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10)
```

*\* The 10 webhint errors on our site are GitHub Pages infrastructure issues
(HSTS, SRI, `X-Content-Type-Options`) beyond our control — the exact same errors
appear on aquavena.nc, as they relate to server configuration, not HTML content.*

# Comparison

```{r compare-plot, fig.height=3.5, fig.width=7}
compare_df <- dbGetQuery(con, "
  SELECT site, MAX(lighthouse_score) AS lh_score
  FROM lighthouse_audits
  GROUP BY site
") |>
  left_join(
    dbGetQuery(con, "
      SELECT site, COUNT(*) AS pa11y_errors
      FROM pa11y_issues
      WHERE type = 'error'
      GROUP BY site
    "),
    by = "site"
  ) |>
  mutate(
    site = recode(site, "our-site" = "Our site", "aquavena.nc" = "aquavena.nc"),
    pa11y_errors = replace_na(pa11y_errors, 0L)
  )

colours <- c("Our site" = "#0f766e", "aquavena.nc" = "#9ca3af")

p1 <- ggplot(compare_df, aes(x = site, y = lh_score, fill = site)) +
  geom_col(width = 0.5, show.legend = FALSE) +
  geom_text(aes(label = lh_score), vjust = -0.4, fontface = "bold", size = 4) +
  scale_fill_manual(values = colours) +
  scale_y_continuous(limits = c(0, 115)) +
  labs(title = "Lighthouse Score", x = NULL, y = "Score / 100") +
  theme(axis.text.x = element_text(face = "bold"))

p2 <- ggplot(compare_df, aes(x = site, y = pa11y_errors, fill = site)) +
  geom_col(width = 0.5, show.legend = FALSE) +
  geom_text(aes(label = pa11y_errors), vjust = -0.4, fontface = "bold", size = 4) +
  scale_fill_manual(values = colours) +
  scale_y_continuous(limits = c(0, 80)) +
  labs(title = "WCAG 2.1 AA Errors (pa11y)", x = NULL, y = "Number of errors") +
  theme(axis.text.x = element_text(face = "bold"))

p1 + p2
```

# Accessibility Features

```{r features-table}
features <- tibble(
  Feature                         = c(
    "WCAG 2.1 AA — 0 errors",
    "Lighthouse 100/100",
    "Atkinson Hyperlegible font",
    "Adjustable text size (A+ / A−)",
    "Dark mode",
    "Text-to-speech (Web Speech API)",
    "PWA — installable, works offline",
    "RSS feeds per diet",
    "iCal calendars per diet",
    "Claude skill (MCP)"
  ),
  `Our site`    = rep("Yes", 10),
  `aquavena.nc` = rep("No",  10)
)
kable(features, booktabs = TRUE, linesep = "", align = c("l", "c", "c")) |>
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10)
```

# Lighthouse History

```{r history-plot}
lh_history <- dbGetQuery(con, "
  SELECT audit_date, lighthouse_score, site
  FROM (
    SELECT audit_date, lighthouse_score, site,
           ROW_NUMBER() OVER (PARTITION BY site, audit_date ORDER BY audit_date) AS rn
    FROM lighthouse_audits
    WHERE audit_id IS NULL OR score IS NOT NULL
  )
  WHERE rn = 1
  ORDER BY site, audit_date
")

if (nrow(lh_history) >= 2) {
  ggplot(lh_history, aes(x = as.Date(audit_date), y = lighthouse_score,
                          color = site, group = site)) +
    geom_line(linewidth = 1) +
    geom_point(size = 3) +
    scale_color_manual(
      values = c("our-site" = "#0f766e", "aquavena.nc" = "#9ca3af"),
      labels = c("our-site" = "Our site", "aquavena.nc" = "aquavena.nc")
    ) +
    scale_y_continuous(limits = c(80, 105)) +
    scale_x_date(date_labels = "%d %b") +
    labs(title = "Lighthouse Score Over Time", x = NULL,
         y = "Score / 100", color = "Site") +
    theme(legend.position = "bottom")
} else {
  cat("*(Not enough history yet — re-run the report on multiple dates to see trends.)*")
}
```

```{r disconnect}
dbDisconnect(con)
```

# Database

All audit results are persisted in **`benchmark/data/benchmark.duckdb`**, a portable
single-file analytical database. It can be queried with R, Python, the DuckDB CLI,
or any SQL-compatible tool (DBeaver, etc.).

## Schema

### Table `pa11y_issues`

Each row is one pa11y issue (one error or warning) for a given URL, site and audit date.

```{=latex}
\begin{center}
\begin{tabular}{llll}
\toprule
\textbf{Column} & \textbf{Type} & \textbf{Nullable} & \textbf{Description} \\
\midrule
\texttt{url}        & VARCHAR   & no  & Page URL audited \\
\texttt{type}       & VARCHAR   & yes & \texttt{error}, \texttt{warning}, \texttt{notice} \\
\texttt{message}    & VARCHAR   & yes & Human-readable issue description \\
\texttt{code}       & VARCHAR   & yes & WCAG rule code (e.g. \texttt{WCAG2AA.Principle1...}) \\
\texttt{site}       & VARCHAR   & no  & \texttt{our-site} or \texttt{aquavena.nc} \\
\texttt{audit\_date}& DATE      & no  & Date the audit was run \\
\bottomrule
\end{tabular}
\end{center}
```

### Table `lighthouse_audits`

Each row is one Lighthouse audit check for a given site and audit date.

```{=latex}
\begin{center}
\begin{tabular}{llll}
\toprule
\textbf{Column} & \textbf{Type} & \textbf{Nullable} & \textbf{Description} \\
\midrule
\texttt{audit\_id}        & VARCHAR & yes & Lighthouse audit identifier \\
\texttt{title}            & VARCHAR & yes & Human-readable audit name \\
\texttt{score}            & DOUBLE  & yes & Audit score: 0.0 (fail), 1.0 (pass), NULL (N/A) \\
\texttt{score\_mode}      & VARCHAR & yes & \texttt{binary}, \texttt{notApplicable}, etc. \\
\texttt{site}             & VARCHAR & no  & \texttt{our-site} or \texttt{aquavena.nc} \\
\texttt{audit\_date}      & DATE    & no  & Date the audit was run \\
\texttt{lighthouse\_score}& INTEGER & no  & Overall page accessibility score (0–100) \\
\bottomrule
\end{tabular}
\end{center}
```

## Example queries

```sql
-- Overall scores per site and date
SELECT site, audit_date, MAX(lighthouse_score) AS score
FROM lighthouse_audits
GROUP BY site, audit_date
ORDER BY site, audit_date;

-- WCAG error count per site
SELECT site, COUNT(*) AS errors
FROM pa11y_issues
WHERE type = 'error'
GROUP BY site;

-- Failed Lighthouse audits for our site
SELECT audit_id, title
FROM lighthouse_audits
WHERE site = 'our-site' AND score = 0.0;
```

# Conclusion

```{r conclusion-vals}
verdict <- if (isTRUE(total_errors == 0) && isTRUE(lh_score_val == 100)) "perfect" else "needs improvement"
```

The site achieves a **`r verdict`** accessibility score:
**`r total_errors` WCAG error(s)** and **Lighthouse `r lh_score_val`/100**.

Compared to aquavena.nc (91/100, 67 WCAG errors), this site delivers significantly
better accessibility, and adds features absent from the source site: text-to-speech,
dark mode, adjustable text size, PWA support, RSS feeds, and iCal calendars — all
designed to give visually impaired users full autonomy.

---

*Report generated on `r format(Sys.Date(), "%B %d, %Y")` · Quarto `r system("quarto --version", intern=TRUE)` · R `r R.version$major`.`r R.version$minor`*
