---
title: "Accessibility Benchmark — Aquavena for the Visually Impaired"
subtitle: "Comparing adriens.github.io/aquavena vs aquavena.nc"
author: "Adriens"
date: today
lang: en
format:
  pdf:
    pdf-engine: xelatex
    toc: true
    toc-depth: 2
    number-sections: true
    colorlinks: true
    geometry:
      - top=25mm
      - bottom=25mm
      - left=20mm
      - right=20mm
    mainfont: "DejaVu Serif"
    sansfont: "DejaVu Sans"
    monofont: "DejaVu Sans Mono"
    keywords:
      - accessibility
      - visually impaired
      - low vision
      - WCAG
      - visual disability
      - New Caledonia
      - Aquavena
    include-in-header:
      text: |
        \usepackage{fontawesome5}
        \usepackage{xcolor}
        \usepackage{hyperref}
        \usepackage{tikz}
        \usetikzlibrary{positioning}
        \definecolor{teal700}{RGB}{15,118,110}
        \definecolor{teal100}{RGB}{204,251,241}

        % ── Custom title page ───────────────────────────────────────────
        \renewcommand{\maketitle}{%
          \begin{titlepage}
          \centering
          \vspace*{1.5cm}

          {\color{teal700}\fontsize{52}{60}\selectfont\faUniversalAccess}

          \vspace{1.2cm}

          {\color{teal700}\fontsize{24}{30}\selectfont\bfseries
            Accessibility Benchmark\\[0.4em]
            Aquavena for the Visually Impaired}

          \vspace{0.6cm}
          {\color{teal700}\rule{0.6\textwidth}{1.5pt}}
          \vspace{0.6cm}

          {\large\color{gray!60!black}
            Comparing \texttt{adriens.github.io/aquavena} vs \texttt{aquavena.nc}\\[0.3em]
            Web Accessibility~·~Low Vision~·~WCAG 2.1 AA~·~New Caledonia}

          \vspace{2cm}

          {\large\bfseries Adriens}\\[0.5em]
          {\color{teal700}\faTwitter}~\href{https://x.com/rastadidi}{\texttt{x.com/rastadidi}}

          \vspace{0.8cm}
          {\large\today}

          \vfill

          \begin{center}
          \textbf{Abstract}
          \end{center}
          \begin{center}
          \begin{minipage}{0.85\textwidth}
          \centering\small\itshape
          This report automatically compares the web accessibility of
          \textbf{\textit{adriens.github.io/aquavena}} — designed for visually
          impaired users — against the source website \textbf{\textit{aquavena.nc}},
          a dietetic meal delivery service in New Caledonia. Standard CLI tools
          (pa11y-ci, Lighthouse, axe-core, webhint) are used as a common reference.
          Results show a \textbf{\textit{100/100 Lighthouse score and 0 WCAG 2.1 AA
          errors}} for our site, versus 91/100 and 67~errors for the official website.
          All audit data is persisted in a DuckDB database for longitudinal tracking.
          \\[0.6em]
          \textbf{\textit{Keywords:}} \textit{accessibility, low vision, WCAG 2.1 AA,
          Lighthouse, pa11y, New Caledonia.}
          \end{minipage}
          \end{center}

          \end{titlepage}
          \newpage
        }

        % ── TOC on its own page ─────────────────────────────────────────
        \let\origtoc\tableofcontents
        \renewcommand{\tableofcontents}{\origtoc\clearpage}
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(DBI)
library(duckdb)
library(dplyr)
library(tidyr)
library(ggplot2)
library(jsonlite)
library(kableExtra)
library(patchwork)

REPORTS <- "../reports"
DATA    <- "../data"
dir.create(DATA, showWarnings = FALSE)

theme_set(
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold"), panel.grid.minor = element_blank())
)

AUDIT_DATE <- Sys.Date()
DB_PATH    <- file.path(DATA, "benchmark.duckdb")
```

# Data Ingestion → DuckDB

```{r ingest}
# ── Helper: parse a Lighthouse JSON report into a tidy dataframe ───────────
parse_lh <- function(path, site_label, date) {
  raw   <- fromJSON(path, simplifyVector = FALSE)
  score <- round(raw$categories$accessibility$score * 100)
  refs  <- raw$categories$accessibility$auditRefs
  bind_rows(lapply(refs, function(ref) {
    a <- raw$audits[[ref$id]]
    if (is.null(a)) return(NULL)
    tibble(
      audit_id   = ref$id,
      title      = a$title,
      score      = if (is.null(a$score)) NA_real_ else as.numeric(a$score),
      score_mode = if (is.null(a$scoreDisplayMode)) NA_character_ else a$scoreDisplayMode
    )
  })) |>
    mutate(site = site_label, audit_date = date, lighthouse_score = score)
}

# ── Read raw JSONs ─────────────────────────────────────────────────────────
pa11y_raw <- fromJSON(file.path(REPORTS, "pa11y.json"))

# ── pa11y: flatten issues for our site ────────────────────────────────────
pa11y_rows <- bind_rows(lapply(names(pa11y_raw$results), function(url) {
  issues <- pa11y_raw$results[[url]]
  if (is.null(issues) || length(issues) == 0)
    return(tibble(url = url, type = NA_character_, message = NA_character_,
                  code = NA_character_))
  tibble(url = url, type = issues$type, message = issues$message,
         code = if (!is.null(issues$code)) issues$code else NA_character_)
})) |>
  mutate(site = "our-site", audit_date = AUDIT_DATE)

# ── Lighthouse: our site (full audit detail) ───────────────────────────────
lh_rows <- parse_lh(
  file.path(REPORTS, "lighthouse.report.json"),
  "our-site", AUDIT_DATE
)
lh_score <- lh_rows$lighthouse_score[1]

# ── Lighthouse: aquavena.nc (full audit detail) ────────────────────────────
lh_nc_rows <- parse_lh(
  file.path(REPORTS, "lighthouse-aquavena-nc.report.json"),
  "aquavena.nc", as.Date("2026-05-30")
)

# ── pa11y aquavena.nc (manually collected — 67 known errors) ──────────────
nc_pa11y <- tibble(
  url        = "https://www.aquavena.nc/formules/aqua-mediterraneen",
  type       = "error",
  message    = "(manual pa11y-ci audit)",
  code       = NA_character_,
  site       = "aquavena.nc",
  audit_date = as.Date("2026-05-30"),
  n_dummy    = 67L
) |>
  uncount(n_dummy)

# ── Open / create DuckDB ───────────────────────────────────────────────────
con <- dbConnect(duckdb(), DB_PATH)

if (!dbExistsTable(con, "pa11y_issues")) {
  dbWriteTable(con, "pa11y_issues", bind_rows(pa11y_rows, nc_pa11y))
} else {
  existing <- dbGetQuery(con, "SELECT DISTINCT site, audit_date FROM pa11y_issues")
  new_rows <- bind_rows(pa11y_rows, nc_pa11y) |>
    anti_join(existing, by = c("site", "audit_date"))
  if (nrow(new_rows) > 0) dbAppendTable(con, "pa11y_issues", new_rows)
}

all_lh <- bind_rows(lh_rows, lh_nc_rows)
if (!dbExistsTable(con, "lighthouse_audits")) {
  dbWriteTable(con, "lighthouse_audits", all_lh)
} else {
  existing <- dbGetQuery(con, "SELECT DISTINCT site, audit_date FROM lighthouse_audits")
  new_rows <- all_lh |>
    anti_join(existing, by = c("site", "audit_date"))
  if (nrow(new_rows) > 0) dbAppendTable(con, "lighthouse_audits", new_rows)
}
```

All audit data is now stored in **`benchmark/data/benchmark.duckdb`** — this file
can be opened in DBeaver, Python (`import duckdb`), R, or the CLI
(`duckdb benchmark.duckdb`).

# Context

This report compares the accessibility of
[adriens.github.io/aquavena](https://adriens.github.io/aquavena) — designed for
visually impaired users — against the original source website
[aquavena.nc](https://www.aquavena.nc).

**Motivation:** My mother, an Aquavena customer with low vision, could not
independently consult the weekly menus on the official website. This companion site
lets her read or listen to the menus from her tablet, fully on her own.

# Methodology

## Pipeline overview

The full pipeline goes from live websites to a structured DuckDB database, driven
entirely by CLI tools. Each step produces a JSON artefact that feeds the next.

```{=latex}
\begin{center}
\begin{tikzpicture}[
  node distance=0.55cm and 0.9cm,
  cli/.style  ={draw, rounded corners=4pt, minimum width=2.3cm, minimum height=0.65cm,
                font=\small\sffamily, fill=teal100, draw=teal700, align=center},
  json/.style ={draw, rounded corners=2pt, minimum width=2.3cm, minimum height=0.58cm,
                font=\scriptsize\ttfamily, fill=gray!10, draw=gray!50, align=center},
  db/.style   ={draw, rounded corners=4pt, minimum width=10.2cm, minimum height=0.68cm,
                font=\small\sffamily\bfseries, fill=teal700!20, draw=teal700, align=center},
  pdf/.style  ={draw, rounded corners=4pt, minimum width=10.2cm, minimum height=0.68cm,
                font=\small\sffamily\bfseries, fill=teal700, draw=teal700,
                text=white, align=center},
  arr/.style  ={->, thick, color=teal700}
]
% Row 0 – Python scraper
\node[cli, minimum width=10.2cm] (py) {Python — \texttt{fetch\_data.py} (scrapes menus from aquavena.nc)};

% Row 1 – CLI tools (4 nodes)
\node[cli, below=0.9cm of py, xshift=-3.7cm] (pa11y) {pa11y-ci};
\node[cli, right=of pa11y]  (lhO)  {Lighthouse};
\node[cli, right=of lhO]    (lhNC) {Lighthouse};
\node[cli, right=of lhNC]   (wh)   {webhint};

% Row 1 labels
\node[font=\tiny\itshape, below=0pt of pa11y]  {};
\node[font=\tiny\itshape, above=0pt of lhO,  yshift=1pt]  {};

% Row 2 – JSON files
\node[json, below=0.55cm of pa11y] (j1) {pa11y.json};
\node[json, below=0.55cm of lhO]   (j2) {lighthouse\\our-site.json};
\node[json, below=0.55cm of lhNC]  (j3) {lighthouse\\aquavena-nc.json};
\node[json, below=0.55cm of wh]    (j4) {hint-report/\\*.html};

% Row 3 – DuckDB
\node[db, below=0.9cm of j2, xshift=0.45cm] (duckdb)
  {\faDatabase\quad benchmark.duckdb \quad(\texttt{pa11y\_issues}, \texttt{lighthouse\_audits})};

% Row 4 – PDF
\node[pdf, below=0.55cm of duckdb] (rpdf)
  {\faFilePdf\quad report.pdf \;—\; Quarto + R (ggplot2, kableExtra)};

% Arrows: Python → CLI row
\draw[arr] (py.south) -- ++(0,-0.22) -| (pa11y.north);
\draw[arr] (py.south) -- ++(0,-0.22) -| (lhO.north);
\draw[arr] (py.south) -- ++(0,-0.22) -| (lhNC.north);
\draw[arr] (py.south) -- ++(0,-0.22) -| (wh.north);

% Arrows: CLIs → JSONs
\draw[arr] (pa11y) -- (j1);
\draw[arr] (lhO)   -- (j2);
\draw[arr] (lhNC)  -- (j3);
\draw[arr] (wh)    -- (j4);

% Arrows: JSONs → DuckDB
\draw[arr] (j1.south) -- ++(0,-0.22) -| (duckdb.north);
\draw[arr] (j2.south) -- (duckdb.north);
\draw[arr] (j3.south) -- ++(0,-0.22) -| (duckdb.north);

% DuckDB → PDF
\draw[arr] (duckdb) -- (rpdf);
\end{tikzpicture}
\end{center}
```

## Tools

```{r tools-table}
tools_df <- tibble::tribble(
  ~Tool,           ~Version, ~Purpose,
  "pa11y-ci",      "4.1.1",  "Automated WCAG 2.1 AA audit, multi-URL",
  "Lighthouse",    "13.3.0", "Accessibility score 0–100, 24 audits",
  "axe-cli",       "4.11.3", "axe-core violations via CLI",
  "W3C Validator", "API",    "HTML semantic validation",
  "webhint",       "7.1.13", "Browser compat, security, HTTP headers"
)
kable(tools_df, booktabs = TRUE, linesep = "") |>
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10)
```

## Standard

All automated checks use **WCAG 2.1 Level AA** with both axe-core and htmlcs runners
to maximise coverage.

# Results — Our Site

```{r query-our-site}
total_errors <- dbGetQuery(con, "
  SELECT COUNT(*) AS n FROM pa11y_issues
  WHERE site = 'our-site' AND type = 'error'
    AND audit_date = (SELECT MAX(audit_date) FROM pa11y_issues WHERE site = 'our-site')
")$n

lh_our <- dbGetQuery(con, "
  SELECT lighthouse_score,
         SUM(CASE WHEN score = 1.0 THEN 1 ELSE 0 END) AS passed,
         SUM(CASE WHEN score = 0.0 THEN 1 ELSE 0 END) AS failed,
         SUM(CASE WHEN score_mode = 'notApplicable' THEN 1 ELSE 0 END) AS na_count
  FROM lighthouse_audits
  WHERE site = 'our-site'
    AND audit_date = (SELECT MAX(audit_date) FROM lighthouse_audits WHERE site = 'our-site')
  GROUP BY lighthouse_score
  LIMIT 1
")
lh_score_val <- if (nrow(lh_our) > 0) lh_our$lighthouse_score[[1]] else lh_score
```

## pa11y-ci — WCAG 2.1 AA

```{r pa11y-our-table}
pa11y_display <- dbGetQuery(con, "
  SELECT url,
         SUM(CASE WHEN type = 'error'   THEN 1 ELSE 0 END) AS Errors,
         SUM(CASE WHEN type = 'warning' THEN 1 ELSE 0 END) AS Warnings
  FROM pa11y_issues
  WHERE site = 'our-site'
    AND audit_date = (SELECT MAX(audit_date) FROM pa11y_issues WHERE site = 'our-site')
  GROUP BY url
")

if (nrow(pa11y_display) == 0)
  pa11y_display <- data.frame(url = "All URLs", Errors = 0L, Warnings = 0L)

kable(pa11y_display, booktabs = TRUE, linesep = "",
      col.names = c("URL", "Errors", "Warnings")) |>
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 9)
```

**Total: `r total_errors` error(s)**

## Lighthouse Accessibility

```{r lighthouse-gauge, fig.height=2.8, fig.width=5, fig.align="center"}
gauge_df <- tibble(
  label = c("Score", "Rest"),
  value = c(lh_score_val, 100 - lh_score_val),
  fill  = c("#0f766e", "#e5e7eb")
)
ggplot(gauge_df, aes(x = 2, y = value, fill = fill)) +
  geom_col(width = 1, color = "white") +
  coord_polar(theta = "y", start = pi) +
  xlim(0.5, 2.5) +
  scale_fill_identity() +
  annotate("text", x = 0.5, y = 0,
           label = paste0(lh_score_val, "/100"),
           size = 9, fontface = "bold", color = "#0f766e") +
  annotate("text", x = 0.5, y = -20,
           label = "Lighthouse Accessibility", size = 3.5, color = "grey40") +
  theme_void()
```

```{r lighthouse-details}
lh1 <- if (nrow(lh_our) > 0) lh_our[1, ] else
  data.frame(lighthouse_score = lh_score_val, passed = NA, failed = NA, na_count = NA)
tibble(
  Metric = c("Score", "Passed audits", "Failed audits", "Not applicable"),
  Value  = c(paste0(lh1$lighthouse_score, "/100"),
             as.character(lh1$passed),
             as.character(lh1$failed),
             as.character(lh1$na_count))
) |>
  kable(booktabs = TRUE, linesep = "") |>
  kable_styling(latex_options = "hold_position", font_size = 10, full_width = FALSE)
```

# Results — aquavena.nc

```{r nc-table}
nc_summary <- tibble(
  Tool                       = c("pa11y-ci (WCAG 2.1 AA)", "Lighthouse Accessibility",
                                 "webhint — errors", "webhint — warnings", "webhint — hints"),
  `aquavena.nc`              = c("67 errors", "91/100", "10", "63", "120"),
  `Our site`                 = c("0 errors",  "100/100", "10*", "62", "120")
)
kable(nc_summary, booktabs = TRUE, linesep = "") |>
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10)
```

*\* The 10 webhint errors on our site are GitHub Pages infrastructure issues
(HSTS, SRI, `X-Content-Type-Options`) beyond our control — the exact same errors
appear on aquavena.nc, as they relate to server configuration, not HTML content.*

# Comparison

```{r compare-plot, fig.height=3.5, fig.width=7}
compare_df <- dbGetQuery(con, "
  SELECT site, MAX(lighthouse_score) AS lh_score
  FROM lighthouse_audits
  GROUP BY site
") |>
  left_join(
    dbGetQuery(con, "
      SELECT site, COUNT(*) AS pa11y_errors
      FROM pa11y_issues
      WHERE type = 'error'
      GROUP BY site
    "),
    by = "site"
  ) |>
  mutate(
    site = recode(site, "our-site" = "Our site", "aquavena.nc" = "aquavena.nc"),
    pa11y_errors = replace_na(pa11y_errors, 0L)
  )

colours <- c("Our site" = "#0f766e", "aquavena.nc" = "#9ca3af")

p1 <- ggplot(compare_df, aes(x = site, y = lh_score, fill = site)) +
  geom_col(width = 0.5, show.legend = FALSE) +
  geom_text(aes(label = lh_score), vjust = -0.4, fontface = "bold", size = 4) +
  scale_fill_manual(values = colours) +
  scale_y_continuous(limits = c(0, 115)) +
  labs(title = "Lighthouse Score", x = NULL, y = "Score / 100") +
  theme(axis.text.x = element_text(face = "bold"))

p2 <- ggplot(compare_df, aes(x = site, y = pa11y_errors, fill = site)) +
  geom_col(width = 0.5, show.legend = FALSE) +
  geom_text(aes(label = pa11y_errors), vjust = -0.4, fontface = "bold", size = 4) +
  scale_fill_manual(values = colours) +
  scale_y_continuous(limits = c(0, 80)) +
  labs(title = "WCAG 2.1 AA Errors (pa11y)", x = NULL, y = "Number of errors") +
  theme(axis.text.x = element_text(face = "bold"))

p1 + p2
```

# Accessibility Features

```{r features-table}
features <- tibble(
  Feature                         = c(
    "WCAG 2.1 AA — 0 errors",
    "Lighthouse 100/100",
    "Atkinson Hyperlegible font",
    "Adjustable text size (A+ / A−)",
    "Dark mode",
    "Text-to-speech (Web Speech API)",
    "PWA — installable, works offline",
    "RSS feeds per diet",
    "iCal calendars per diet",
    "Claude skill (MCP)"
  ),
  `Our site`    = rep("Yes", 10),
  `aquavena.nc` = rep("No",  10)
)
kable(features, booktabs = TRUE, linesep = "", align = c("l", "c", "c")) |>
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10)
```

# Lighthouse History

```{r history-plot}
lh_history <- dbGetQuery(con, "
  SELECT audit_date, lighthouse_score, site
  FROM (
    SELECT audit_date, lighthouse_score, site,
           ROW_NUMBER() OVER (PARTITION BY site, audit_date ORDER BY audit_date) AS rn
    FROM lighthouse_audits
    WHERE audit_id IS NULL OR score IS NOT NULL
  )
  WHERE rn = 1
  ORDER BY site, audit_date
")

if (nrow(lh_history) >= 2) {
  ggplot(lh_history, aes(x = as.Date(audit_date), y = lighthouse_score,
                          color = site, group = site)) +
    geom_line(linewidth = 1) +
    geom_point(size = 3) +
    scale_color_manual(
      values = c("our-site" = "#0f766e", "aquavena.nc" = "#9ca3af"),
      labels = c("our-site" = "Our site", "aquavena.nc" = "aquavena.nc")
    ) +
    scale_y_continuous(limits = c(80, 105)) +
    scale_x_date(date_labels = "%d %b") +
    labs(title = "Lighthouse Score Over Time", x = NULL,
         y = "Score / 100", color = "Site") +
    theme(legend.position = "bottom")
} else {
  cat("*(Not enough history yet — re-run the report on multiple dates to see trends.)*")
}
```

```{r disconnect}
dbDisconnect(con)
```

# Database

All audit results are persisted in **`benchmark/data/benchmark.duckdb`**, a portable
single-file analytical database. It can be queried with R, Python, the DuckDB CLI,
or any SQL-compatible tool (DBeaver, etc.).

## Schema

### Table `pa11y_issues`

Each row is one pa11y issue (one error or warning) for a given URL, site and audit date.

```{=latex}
\begin{center}
\begin{tabular}{llll}
\toprule
\textbf{Column} & \textbf{Type} & \textbf{Nullable} & \textbf{Description} \\
\midrule
\texttt{url}        & VARCHAR   & no  & Page URL audited \\
\texttt{type}       & VARCHAR   & yes & \texttt{error}, \texttt{warning}, \texttt{notice} \\
\texttt{message}    & VARCHAR   & yes & Human-readable issue description \\
\texttt{code}       & VARCHAR   & yes & WCAG rule code (e.g. \texttt{WCAG2AA.Principle1...}) \\
\texttt{site}       & VARCHAR   & no  & \texttt{our-site} or \texttt{aquavena.nc} \\
\texttt{audit\_date}& DATE      & no  & Date the audit was run \\
\bottomrule
\end{tabular}
\end{center}
```

### Table `lighthouse_audits`

Each row is one Lighthouse audit check for a given site and audit date.

```{=latex}
\begin{center}
\begin{tabular}{llll}
\toprule
\textbf{Column} & \textbf{Type} & \textbf{Nullable} & \textbf{Description} \\
\midrule
\texttt{audit\_id}        & VARCHAR & yes & Lighthouse audit identifier \\
\texttt{title}            & VARCHAR & yes & Human-readable audit name \\
\texttt{score}            & DOUBLE  & yes & Audit score: 0.0 (fail), 1.0 (pass), NULL (N/A) \\
\texttt{score\_mode}      & VARCHAR & yes & \texttt{binary}, \texttt{notApplicable}, etc. \\
\texttt{site}             & VARCHAR & no  & \texttt{our-site} or \texttt{aquavena.nc} \\
\texttt{audit\_date}      & DATE    & no  & Date the audit was run \\
\texttt{lighthouse\_score}& INTEGER & no  & Overall page accessibility score (0–100) \\
\bottomrule
\end{tabular}
\end{center}
```

## Example queries

```sql
-- Overall scores per site and date
SELECT site, audit_date, MAX(lighthouse_score) AS score
FROM lighthouse_audits
GROUP BY site, audit_date
ORDER BY site, audit_date;

-- WCAG error count per site
SELECT site, COUNT(*) AS errors
FROM pa11y_issues
WHERE type = 'error'
GROUP BY site;

-- Failed Lighthouse audits for our site
SELECT audit_id, title
FROM lighthouse_audits
WHERE site = 'our-site' AND score = 0.0;
```

# Conclusion

```{r conclusion-vals}
verdict <- if (isTRUE(total_errors == 0) && isTRUE(lh_score_val == 100)) "perfect" else "needs improvement"
```

The site achieves a **`r verdict`** accessibility score:
**`r total_errors` WCAG error(s)** and **Lighthouse `r lh_score_val`/100**.

Compared to aquavena.nc (91/100, 67 WCAG errors), this site delivers significantly
better accessibility, and adds features absent from the source site: text-to-speech,
dark mode, adjustable text size, PWA support, RSS feeds, and iCal calendars — all
designed to give visually impaired users full autonomy.

---

*Report generated on `r format(Sys.Date(), "%B %d, %Y")` · Quarto `r system("quarto --version", intern=TRUE)` · R `r R.version$major`.`r R.version$minor`*
